A weakly structured stem for human origins in Africa

### 2022-02-28 paper.tex
comments on Figure 1

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig1.pdf}
    \caption{
        \textbf{Representative genetic diversity within Africa.}
        (A) Select populations from 1000 Genomes and ADRP illustrate diversity from
        western, eastern and southern Africa. We chose representatives from each region
        to build parameterized models, including the newly-sequenced Nama from South Africa, Mende
        from Sierre Leone, Gumuz, Oromo and Amhara from Ethiopia, and the
        British and Vindija Neanderthal individual (bold fonts). (B, C) PCA highlights the range of genetic divergence anchored 
        by western Africans, Nama, Gumuz and the British. (D) \texttt{ADMIXTURE}
        illustrates signatures of recent gene flow in Africa which reflect colonial-period migration into the Nama,
        Back-to-Africa gene flow among some Ethiopians, and Khoe-San admixture in the Zulu.
    }
    \label{fig:1}
\end{figure}

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig1.pdf}
    \caption{
        \textbf{Genetic diversity across Africa.}
        (A) Select populations from 1000 Genomes and ADRP   \sgcomment{define} illustrate diversity from
        western, eastern and southern Africa. We chose representatives from each region
        to build parameterized models, including the newly-sequenced Nama from South Africa, Mende
        from Sierre Leone, Gumuz, Oromo and Amhara from Ethiopia, and the
        British and Vindija Neanderthal individual (bold fonts \sgcomment{I don't see bold fonts}). (B, C) PCA highlights the range of genetic divergence anchored 
        by western Africans, Nama, Gumuz and the British. \sgcomment{I think we should indicate the origin on PCAS, also possible variance explained.} (D) \texttt{ADMIXTURE}
        illustrates signatures of recent gene flow in Africa which reflect colonial-period migration into the Nama,
        Back-to-Africa gene flow among some Ethiopians, and Khoe-San admixture in the Zulu.
    }
    \label{fig:1}
\end{figure}
